\sysfull

### 2018-04-17 paper/implementation.tex
impl: shorten
impl: typesetting: log not the product of l o and g

Coala's API adds only five syntactic constructs to a C-based language.
\texttt{COALA\_TASK} is a function annotation that declares a function to be a
task. \texttt{COALA\_NEXT\_TASK}, indicates the task to run next, after an
executing task completes.  \texttt{COALA\_PV} declare a new protected variable.
The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
respectively.  \texttt{COALA\_SM} identifies protected \texttt{struct} fields
and tells \sys to ensure that the struct fields are page-aligned in memory.
The programmer is required to explicitly call two API functions at the start of
{\tt main()}: \texttt{COALA\_INIT}, which does global initialization upon first
boot and \texttt{COALA\_RUN} which hands the control to \sys's task manager to
resume task execution.

Table~\ref{table:coala_api} summarizes \sys's API methods and their arguments.

@@

To access a protected variable with either \texttt{RP}
or \texttt{WP}, \sys searches for the variable in its working buffer first. If
found, the program accesses the data in the working buffer.  If the page is not 
in the working memory, the memory manager fetches it from non-volatile memory. 
%
\sys uses address-based page tagging to make finding a variable efficient.  The
upper bits of a variable's memory address identify its page, and the lower bits
denote the variable's offset in its page. The total number of pages in memory,
$p$, determines the number of tag bits, which is $log(P)$.

>>>>

Coala's API adds only five syntactic constructs to a C-based language, summarized
in Table~\ref{table:coala_api}.
\texttt{COALA\_TASK} is a function annotation that declares a function to be a
task. \texttt{COALA\_NEXT\_TASK}, indicates the task to run next, after an
executing task completes.  \texttt{COALA\_PV} declare a new protected variable.
The programmer uses \texttt{RP} and \texttt{WP}, to read and write protected
respectively.  \texttt{COALA\_SM} identifies protected \texttt{struct} fields
and tells \sys to ensure that the struct fields are page-aligned in memory.
The programmer is required to explicitly call two API functions at the start of
{\tt main()}: \texttt{COALA\_INIT}, which does global initialization upon first
boot and \texttt{COALA\_RUN} which hands the control to \sys's task manager to
resume task execution.

@@

To access a protected variable with either \texttt{RP}
or \texttt{WP}, \sys searches for the variable in its working buffer first. If
found, the program accesses the data in the working buffer.  If the page is not 
in the working memory, the memory manager fetches it from non-volatile memory. 
%
\sys uses address-based page tagging to make finding a variable efficient.  The
upper bits of a variable's memory address identify its page, and the lower bits
denote the variable's offset in its page. The total number of pages in memory,
$p$, determines the number of tag bits, which is $\log P$.
